Nock for Everyday Coders

### 2025-04-23 mss.tex
Change affiliation

\newcommand{\authorname}{Tim Galebach}
\newcommand{\authorpatp}{\patp{timluc-miptev}}
\newcommand{\affiliation}{Uncentered Systems}

@@

\begin{lstlisting}[style=listingcode]
*[a @9@ b c]       *[*[a c] @2@ [@0@ 1] 0 b]
\end{lstlisting}

@@

When I first say \lstinline[style=inlinecode]{@9@}, I thought: ``why didn't they just use \lstinline[style=inlinecode]{@2@} to make the transformed subject? Why is there an extra step to use \lstinline[style=inlinecode]{[@0@ 1]} to pull the new \lstinline[style=inlinecode]{*[a c]} subject? Why can't we do \lstinline[style=inlinecode]{*[a @2@ c [@0@ b]]}?

>>>>

\newcommand{\authorname}{Tim Galebach}
\newcommand{\authorpatp}{\patp{timluc-miptev}}
\newcommand{\affiliation}{Hyperware}

@@

\begin{lstlisting}[style=listingcode]
*[a @9@ b c]       *[*[a c] @2@ [@0@ 1] @0@ b]
\end{lstlisting}

@@

When I first saw \lstinline[style=inlinecode]{@9@}, I thought: ``why didn't they just use \lstinline[style=inlinecode]{@2@} to make the transformed subject? Why is there an extra step to use \lstinline[style=inlinecode]{[@0@ 1]} to pull the new \lstinline[style=inlinecode]{*[a c]} subject? Why can't we do \lstinline[style=inlinecode]{*[a @2@ c [@0@ b]]}?
